Geometric variational problems

### 2020-11-05 NSF2020/Description/specificaim3_ver2.tex
fixed bib file

The most significant challenges of a BIE formulation include solving
dense linear systems, developing preconditioning strategies, and
developing quadrature methods for integrands that are nearly singular.
These challenges are described in section~\ref{subsec:NumericalIssues}.
Then, in section~\ref{subsec:timeStepping}, time stepping strategies are
described, and stable BIE formulations for fluctuating hydrodynamics are
in section~\label{subsec:fluctuating}.

>>>>

The most significant challenges of a BIE formulation include solving
dense linear systems, developing preconditioning strategies, and
developing quadrature methods for integrands that are nearly singular.
These challenges are described in section~\ref{subsec:NumericalIssues}.
Then, in section~\ref{subsec:timeStepping}, time stepping strategies are
described, and stable BIE formulations for fluctuating hydrodynamics are
in section~\ref{subsec:fluctuating}.
